OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-11-25 manuscript_nar.tex
Minor changes.

The experimental biases are estimated genome-wide and each cell of the
Hi-C matrix is then corrected using equation (\ref{eq:xhat}). Note that
the corrected contact profile is still proportional to the copy number.
In cancer cell lines, the contact profile corrected by \textit{OneD} is
highly correlated to the copy number estimated from an external source
(Supplementary Figure~1). Figure~\ref{fig:totals}B shows the corrected
contact profile along chromosome 17 of T47D. \textit{OneD} greatly reduces
the wiggling of the contact profile (dark blue line).

Optionally, \textit{OneD} allows the user to also correct the Hi-C signal
for the copy number. In this case, a hidden Markov model is fitted on the
corrected contact profile in order to infer the local copy number. Each
cell of the Hi-C matrix is then further corrected using equation
(\ref{eq:cnvnorm}), \textit{i.e.} it is divided by the square root of the
inferred copy number. In essence, this approach flattens the contact
profile so that it is no longer proportional to the local copy number. The
light blue line in figure~\ref{fig:totals}B shows the result of this
process. After this correction, the contact profile fluctuates around a
genome-wide constant value.

>>>>

The experimental biases are estimated genome-wide and each entry of the
Hi-C matrix is then corrected using equation (\ref{eq:xhat}). Note that
the corrected contact profile is still proportional to the copy number.
In cancer cell lines, the contact profile corrected by \textit{OneD} is
highly correlated to the copy number estimated from an external source
(Supplementary Figure~1). Figure~\ref{fig:totals}B shows the corrected
contact profile along chromosome 17 of T47D, where \textit{OneD} greatly
reduces the fluctuations (dark blue line).

Optionally, \textit{OneD} allows the user to also correct the Hi-C signal
for the copy number. In this case, a hidden Markov model is fitted on the
corrected contact profile in order to infer the local copy number. Each
entry of the Hi-C matrix is then further corrected using equation
(\ref{eq:cnvnorm}), \textit{i.e.} it is divided by the square root of the
inferred copy number. In essence, this approach flattens the contact
profile so that it is no longer proportional to the local copy number. The
light blue line in figure~\ref{fig:totals}B shows the result of this
process. After this correction, the contact profile fluctuates around a
genome-wide constant value.
